Precise Data Flow Analysis\\in the Presence of Correlated Method Calls

### 2014-12-12 content/appendix.tex
removing notion of set of functions with given signature; working on proofs

\begin{proof}[\textbf{Proof of Lemma~\ref{lem:subsetifds}}]
  Let $P$ be an IFDS problem. Recall from Section~\ref{sec:ideToIfds} that the result of an IFDS analysis $\resultIFDS(P)$ maps supergraph
  nodes $n\in N^*$ to sets of data-flow facts $\delta\in2^D$. Specifically,
  \begin{equation}
    \resultIFDS(P)=\lambda n\,.\,\mvp F(n).
  \end{equation}
  The transformation $\backCC$ is the same as $\backEq$, except that it can remove data-flow facts from the result:
  \begin{align*}
    \backCC\left(\resultIDE(\transCC_R(P))\right)(n)
    &=\left(\lambda n'\,.\,\left\{d\,|\,\resultIDE(\transCC_R(P))(n')=(d,\,\ell),\,\forall r\,.\,\ell(r)\ne\top_T\right\}\right)(n)\\
    &=\left\{d\,|\,\resultIDE(\transCC_R(P))(n)=(d,\,\ell),\,\forall r\,.\,\ell(r)\ne\top_T\right\}\\
    &\subseteq\left\{d\,|\,\resultIDE(\transCC_R(P))(n)=(d,\,\ell),\,\ell\ne\topcc\right\}\\
    &=\backEq\left(\resultIDE(\transCC_R(P))(n)\right)\,.\qedhere
  \end{align*}
\end{proof}

@@

      \begin{enumerate}
        \item if $r=r'$, then $\efek=\bot_T$, which contains $t'$.
        \item\label{item:defaultmap} If $r\ne r'$, then $r$ has not been reassigned a value, and still maps to the same object of type $t$. The receiver $r$ is mapped to $\Delta(r)$, which, according to~\eqref{eq:deltaContainsT}, contains $t$. Since $t=t'$, $\Delta(r)$ contains $t'$.
      \end{enumerate}
    \item\label{item:callstart} $e_k$ is a call-start edge with signature $s_\mathcal F$, and $f\in\mathcal F$ is the called procedure.
      Then
        \begin{align*}
          \efek
          &=(\lambda m\,.\,m[r'\to m(r')\cap\tau(s_\mathcal F,\,f)])(\Delta)(r)\\
          &=\Delta[r'\to\Delta(r')\cap\tau(s_\mathcal F,\,f)]\,,
        \end{align*}
      where $r'$ is the receiver of the call.
      \begin{itemize}
        \item If $r'=r$, then $\Delta(r')=\Delta(r)$ which contains $t$. Since $t\in\tau(s_\mathcal F,\,f)$, it follows that $t\in\Delta(r)\cap\tau(s_\mathcal F,\,f)$, and $t\in\efek$.
         \item If $r'\ne r$, see~(\ref{item:defaultmap}).
       \end{itemize}
    \item $e_k$ is an end-return edge, $r_1,\,\dots,\,r_k\in R$ are the local variables in the callee method, $r'$ is the receiver of the call site corresponding to the return node $n_k$, and $f\in\mathcal F$ is the called method with signature~$s_\mathcal F$.
      Then 
      \[
        \varepsilon_R(e_k)=\lambda m\,.\,m[r'\to m(r')\cap\tau(s_\mathcal F,\,f)][r_1\to\bot_T]\dots[r_k\to\bot_T].
      \]
      If $r\in\{r_1,\,\dots,\,r_k\}$, see~Case~\ref{item:asgn}. Otherwise, the case is analogous to Case~\ref{item:callstart}.
    \item\label{item:idcase} The node contains any other instruction.
      Then 
      \[
        \ccedgefn R(e_k)(\mpdkm)(r)=\id(\Delta)(r)=\Delta(r),
      \]
      which contains $t$ according to~\eqref{eq:deltaContainsT}.\qedhere
  \end{enumerate}
\end{proof}

@@

    Assume that $e_k$ is a end-return edge with a call on the receiver $r'\in R$ with a signature $s_\mathcal F$ to a function $f\in\mathcal F$.
    \begin{align*}
      \ccedgefn R&(e_k)(\mpdkm)(r)\\
      &=\left(\lambda m\,.\,m[r'\to m(r)\cap\tau(s_\mathcal F,\,f)][r_1\to\bot_T]\dots[r_l\to\bot_T]\right)(\mpdkm)(r)\\
      &=\left(\mpdkm[r'\to \uptau\cap\tau(s_\mathcal F,\,f)][r_1\to\bot_T]\dots[r_l\to\bot_T]\right)(r)\,,
    \end{align*}
  where $r_1,\,\dots,r_l\in R$ are the local variables in the called method.

@@

    Otherwise, if $r=r'$, then $\efek=\uptau\cap\tau(s_\mathcal F,\,f)$.

    According to Lemma~\ref{lem:sound1} and by the induction hypothesis, the runtime type $t$ of $r$ must be contained in $\mpdkm(r)=\uptau$. At the same time, by definition, $t$ is part of $\tau(s_\mathcal F,\,f)$. Therefore, $t\in\uptau\cap\tau(s_\mathcal F,\,f)\subseteq\efek$, which means that $\efek\ne\top_T$.

@@

@@

\begin{proof}[\textbf{Proof of Lemma~\ref{lem:sound}}] Let $\rho=\resultIDE(\transCC_R(P))$. Then
  \begin{align*}
    \backCC(\rho)(n)
    &=D_n^\Subset(\rho)\\
    &=\left\{d'\ |\ 
        d'\in\mvp F(n)\,\wedge\,\forall r\in R:\ \rho(n,\ d')(r)\ne\top_T\right\}.
  \end{align*}
  Since $\mvp F(n)=\bigsqcap_{q\in\ivp(n)}M_F(q)(\varnothing)$, and $p\in\ivp(n)$, it follows that
    \begin{align*}
      d&\in M_F(p)(\varnothing)\\&\subseteq\mvp F(n)\,.
    \end{align*}
  At the same time, for all receivers $r\in R$,
  \begin{align*}
    \rho(n,\,d)(r)
    &=\left(\bigsqcap_{q\in\ivp(n)}\mpddef q d\right)(r)\\
    &=\bigsqcap_{q\in\ivp(n)}\mpddef q d(r)\,.
  \end{align*}
  According to~Lemma~\ref{lem:sound3}, $\mpd(r)\ne\top_T$.
  Since $p\in\ivp(n)$,
  \begin{align*}
    \mpd(r)\subseteq\bigsqcap_{q\in\ivp(n)}\mpddef qd(r)\,.
  \end{align*}
  From $\bigsqcap_{q\in\ivp(n)}\mpddef qd(r)=\rho(n,\,d)(r)$ it follows that
  $\mpd(r)\subseteq\rho(n,\,d)(r)$.
  Therefore, $\rho(n,\,d)(r)\ne\top_T$, and $d\in D_n^\Subset(\rho)=\backCC(\rho)(n)$.
\end{proof}

@@

  Otherwise, there are four sub-cases.
  \begin{enumerate}
    \item $e_k$ is a call-start edge, $r'.c()$ is the call site at $n_{k-1}$ with signature $s_\mathcal F$, $f\in\mathcal F$ is the called procedure, and $r'\in U$.
    Then
    \[
      \ccedgefn U(e_k)=\lambda m\,.\,\delta(m)[r'\to\delta(m)(r)\cap\tau(s_\mathcal F,\,f)]\,.
    \]
    There are two sub-cases.
    \begin{enumerate}
      \item\label{item:callstartreceq} If $r=r'$, then, according to~\eqref{eq:edgefnU}, the resulting set of types 
        \[
          \ccedgefn U(q')(\topcc)(r)=\delta(\ccedgefn U(q)(\topcc))(r)\cap\tau(s_\mathcal F,\,f).
        \]
        If $d_{k-1}=\Lambda$, then $\delta(\ccedgefn U(q)(\topcc))(r)=\botcc(r)=\bot_T$. If $d_{k-1}\ne\Lambda$, then $\delta(\ccedgefn U(q)(\topcc))(r)=\ccedgefn U(q)(\topcc)(r)=\uptau$. The set $\tau(s_\mathcal F,\,f)$ is the same for either case.

        Therefore, the value of $\ccedgefn U(q')(\topcc)(r)$ has the same result regardless of $U$,
        which means that $\ccedgefn S(q')(\topcc)(r)=\ccedgefn{\{r\}}(q')(\topcc)(r)$, and the Lemma holds.
      \item\label{item:callstartrecneq} If $r\ne r'$, then
        \begin{equation}
          \ccedgefn U(q')(\topcc)(r)=\delta(\ccedgefn U(q)(\topcc))(r)\,,
        \end{equation}
        which, as we have seen in~Case~\eqref{item:callstartreceq}, does not depend on~$U$, and the Lemma holds.
    \end{enumerate}
    \item $e_k$ is an end-return edge, $r_1,\,\dots,\,r_l\in U$ are the local variables in the callee method, $r'.c()$ is the call corresponding to the return node at $n_k$, $f\in\mathcal F$ is the called method with signature $s_\mathcal F$, and $r'\in U$.
    Then
    \[
      \ccedgefn U(e_k)=\lambda m\,.\,\delta(m)
      [r'\to\delta(m)(r)\cap\tau(s_\mathcal F,\,f)]
      [r_1\to\bot_T]\ldots[r_l\to\bot_T]\,.
    \]
    There are three sub-cases.
    \begin{enumerate}
      \item\label{item:localvarrec} If $r\in\{r_1,\,\dots,\,r_l\}$, then regardless of the value of $U$,
      \[
        \ccedgefn U(q')(\topcc)(r)=\bot_T\,,
      \]
      and the Lemma holds.
      \item Otherwise, if $r=r'$, the case is analogous to Case~\eqref{item:callstartreceq}.
      \item If $r\notin\{r',\,r_1,\,\dots,\,r_l\}$, then see Case~\eqref{item:callstartrecneq}.
    \end{enumerate}
    \item $n_{k-1}$ contains an assignment for $r'\in U$. Then
    \[
      \ccedgefn U(e_k)=\lambda m\,.\,\delta(m)[r'\to\bot_T]\,.
    \]
    If $r=r'$, see Case~\eqref{item:localvarrec}. If $r\ne r'$, see Case~\eqref{item:callstartrecneq}.
    \item Otherwise,
    \[
      \ccedgefn U(e_k)=\lambda m\,.\,\delta(m)\,,
    \]
    and the case is analogous to Case~\eqref{item:callstartrecneq}.\qedhere
  \end{enumerate}
\end{proof}

@@

\begin{lemma}\label{lem:recindep} Let $P$ be an IFDS problem. Let $N^*$ be the supergraph for $P$, $D$ the set of data-flow facts, and $S\subseteq R$ a set of receivers.
  Then for any $n\in N^*$, $d\in D$, and receiver $r\in S$,
  \begin{equation}
    \resultIDE\left(\transCC_S(P)\right)(n,\,d)(r)=
    \resultIDE(\transCC_{\{r\}}(P))(n,\,d)(r)\,.
  \end{equation}
\end{lemma}
\begin{proof}
 Recall from Section~\ref{sec:ideToIfds} that the result of an IDE analysis maps a lattice element to each node in the exploded supergraph. Specifically, for an IDE problem $Q$, the result $\resultIDE(Q):\ N^\#\to L$ maps nodes of the exploded supergraph to lattice elements:
\begin{equation}\label{eq:ideresult}
  \resultIDE(Q)=\{((n,\,d),\,\mvp{\textsf{Env}}(n,\,d))\ |\ n\in N^*,\,d\in D\}\,.
\end{equation}
Furthermore, recall from Section~\ref{sec:bgide} that
\begin{equation}\label{eq:mvpdef}
  \mvp{\textsf{Env}}(n)=\bigsqcap_{q\in\ivp(n)}M_\textsf{Env}(q)(\top)
\end{equation}

  According to~\eqref{eq:ideresult}, \eqref{eq:mvpdef}, and~\eqref{eq:envTransToEdgeFnEdge},
  \begin{align}
    \resultIDE\left(\transCC_S(P)\right)(n,\,d)(r)
    &=\mvp{\textsf{Env}}(n,\,d)(r)\notag\\
    &=\left(\bigsqcap_{q\in\ivp(n)}M_\textsf{Env}(q)(\Omega)(d)\right)(r)\notag\\
    &=\left(\bigsqcap_{q\in\ivp(n)}\bigsqcap_{q'\in\mathsf{RP}(q,\,d)}\ccedgefn S(q')(\topcc)\right)(r)\notag\\
    &=\bigcup_{q\in\ivp(n)}\bigcup_{q'\in\mathsf{RP}(q,\,d)}\ccedgefn S(q')(\topcc)(r)\,.\label{eq:resultThroughEdgefn}
  \end{align}
  Then from Lemma~\ref{lem:recindepedgefn},
  \begin{align*}
    \resultIDE\left(\transCC_S(P)\right)(n,\,d)(r)
    &=\bigcup_{q\in\ivp(n)}\bigcup_{q'\in\mathsf{RP}(q,\,d)}\ccedgefn{\{r\}}(q')(\topcc)(r)\\
    &=\resultIDE\left(\transCC_{\{r\}}(P)\right)(n,\,d)(r)\,.\qedhere
  \end{align*}
\end{proof}

The next lemma shows that the set of types to which a receiver is mapped in a correlated-calls lattice element can be represented as an intersection of static-type function applications $\tau(s_{\mathcal F_i},\,f_i)$.
\begin{lemma}\label{lem:edgefnThroughTaus}
  For an IFDS problem $P$, a node $n\in N^*$, and fact $d\in D$, let $p\in\mathsf{RP}(n,\,d)$ be a realizable path and $r\in R$ a receiver. Then there exists a non-negative number $\gamma$ of calls on the receiver $r$ with signatures $s_{\mathcal F_\gamma}$ to the functions $f_\gamma\in\mathcal F_\gamma$, for which
  \[
    \ccedgefn{\{r\}}(p)(\topcc)(r)=
      \bigcap_{\gamma\ge0}\tau(s_{\mathcal F_\gamma},\,f_\gamma)\,.
  \]
\end{lemma}
\begin{proof}
  Let $p$ have the following form\footnote{It can be shown from the definition of a pointwise representation in~Sagiv et al.~\cite{sagiv1996precise} that in a realizable path, there is never an edge from a fact of the set $D$ to a $\Lambda$ fact. Therefore, we can represent $p$ as a sequence of nodes that has a prefix of $\Lambda$-fact nodes, after which all nodes are non-$\Lambda$ facts.}:
  \[
    p=[(\startmain,\,\Lambda),\,(n_1,\,\Lambda),\,\dots,\,(n_k,\,\Lambda),
       (n_{k+1},\,d_{k+1}),\,\dots,\,(n_{k+l},\,d_{k+l})]\,,
  \]
  where $l\ge1$ and the facts for all nodes up to $n_k$ are equal to $\Lambda$ and $d_{k+i}\in D$ for $0<i\le l$.

@@

  From~\eqref{eq:edgefndef} we can infer that
  \[
    \ccedgefn{\{r\}}(p)=
    \ccedgefn{\{r\}}(e_{k+l})
    \circ\ldots
    \circ\ccedgefn{\{r\}}(e_{k+2})
    \circ(\lambda m\,.\,\beta)
    \circ\id
    \circ\ldots
    \circ\id\,,
  \]
  where
  \[
    \beta=
    \begin{cases}
      \botcc[r\to\tau(s_\mathcal F,\,f)]&\text{if $(n_k,\,n_{k+1})$ is a call-start or end-return edge, and}\\&\text{the call site $r.c()$ with signature $s_\mathcal F$ to the function}\\
      &\text{$f\in\mathcal F$ corresponds to the call-start or end-return edge,}\\
      \botcc&\text{otherwise\footnotemark.}
    \end{cases}
  \]
  \footnotetext{Since $d_k=\Lambda$ and $d_{k+1}\ne\Lambda$, the micro function for the edge $e_{k+1} $ is equal to $\lambda m\,.\,\varepsilon_{\{r\}}(e_{k+1})(\botcc)$. From the definition of $\varepsilon_S$~\eqref{eq:varepsilon} we can see that the only case where $\varepsilon_{\{r\}}(e_{k+1})(m)$ would not be equal to $\botcc$ is when $e_{k+1}$ is call-start or end-return edge.}

@@

If $\beta=\botcc[r\to\tau(s_\mathcal F,\,f)]$, then 
\[
  \ccedgefn{\{r\}}(p)(\topcc)(r)=\tau(s_\mathcal F,\,f)\,,
\]
and $\gamma=1$.

@@

Otherwise,
\begin{align*}
  \ccedgefn{\{r\}}(e_{k+l+1})(\topcc)(r)&=\ccedgefn{\{r\}}(p)(\topcc)(r)\\
  &=\bigcap_{N}\tau(s_{\mathcal F_N},\,f_N)\,,
\end{align*}
and therefore $\gamma=N$.

Suppose that $e_{k+l+1}$ is a call-start edge with a call on the receiver $r$ with signature $s_\mathcal G$ to a function $g\in\mathcal G$. Then, according to~\eqref{eq:varepsilon}, 
\[
  \ccedgefn{\{r\}}(e_{k+l+1})=\lambda m\,.\,m[r\to m(r)\cap\tau(s_\mathcal G,\,g)]\,.
\]
Therefore,
\begin{align*}
  \ccedgefn{\{r\}}&(p')(\topcc)(r)\\
  &=\lambda m\,.\,m[r\to m(r)\cap\tau(s_\mathcal G,\,g)]\left(\ccedgefn{\{r\}}(p)(\topcc)\right)(r)\\
  &=\ccedgefn{\{r\}}(p)(\topcc)(r)\cap\tau(s_\mathcal G,\,g)\\
  &=\left(\bigcap_{N}\tau(s_{\mathcal F_N},\,f_N)\right)\cap\tau(s_\mathcal G,\,g)\,,
\end{align*}
and the Lemma holds for $\gamma=N+1$.

@@

\begin{proof}[\textbf{Proof of Lemma~\ref{lem:onlycorrrec}}]
  From Section~\ref{sec:ideToIfds} we know that
  \[
    \backCC(\resultIDE\left(\transCC_R(P)\right))
    =\lambda n.\{d\,|\,\resultIDE(\transCC_R(P))(n)=(d,\,\ell),\,\forall r\,.\,\ell(r)\ne\topcc\}\,.
  \]
  We can rewrite this equation as follows:
  \[
    \backCC(\resultIDE\left(\transCC_R(P)\right))
    =\lambda n.\{d\,|\,\forall r,\,\resultIDE(\transCC_R(P))(n)=(d,\,\ell),\,\forall r\,.\,\ell(r)\ne\topcc\}\,.
  \]

>>>>

\begin{proof}[\textbf{Proof of Lemma~\ref{lem:subsetifds}}]
  Let $P$ be an IFDS problem. Recall from Section~\ref{sec:ideToIfds} that the result of an IFDS analysis $\resultIFDS(P)$ maps supergraph
  nodes $n\in N^*$ to sets of data-flow facts $\delta\in2^D$. Specifically,
  \begin{equation}
    \resultIFDS(P)=\lambda n\,.\,\mvp F(n)\,.
  \end{equation}
  The transformation $\backCC$ is the same as $\backEq$, except that it can remove data-flow facts from the result:
  \begin{align*}
    \backCC\left(\resultIDE(\transCC_R(P))\right)(n)
    &=\left(\lambda n'\,.\,\left\{d\,|\,\forall r\in R\,.\,\resultIDE(\transCC_R(P))(n')(d)(r)\ne\top_T\right\}\right)(n)\\
    &=\left\{d\,|\,\forall r\in R\,.\,\resultIDE(\transCC_R(P))(n')(d)(r)\ne\top_T\right\}\\
    &\subseteq\left\{d\,|\,\resultIDE(\transCC_R(P))(n)(d)\ne\topcc\right\}\\
    &=\backEq\left(\resultIDE(\transCC_R(P))(n)\right).\qedhere
  \end{align*}
\end{proof}

@@

      \begin{enumerate}
        \item if $r=r'$, then $\efek=\bot_T$, which contains $t'$.
        \item\label{item:defaultmap} If $r\ne r'$, then $r$ has not been reassigned a value, and still maps to the same object of type $t$. The receiver $r$ is mapped to $\Delta(r)$, which, according to~\eqref{eq:deltaContainsT}, contains $t$. Since $t=t'$, $\Delta(r)$ contains $t'$.
      \end{enumerate}
    \item\label{item:callstart} $e_k$ is a call-start edge with signature $s$, and $f$ is the called procedure.
      Then
        \begin{align*}
          \efek
          &=(\lambda m\,.\,m[r'\to m(r')\cap\tau(s,\,f)])(\Delta)(r)\\
          &=\Delta[r'\to\Delta(r')\cap\tau(s,\,f)]\,,
        \end{align*}
      where $r'$ is the receiver of the call.
      \begin{itemize}
        \item If $r'=r$, then $\Delta(r')=\Delta(r)$ which contains $t$. Since $t\in\tau(s,\,f)$, it follows that $t\in\Delta(r)\cap\tau(s,\,f)$, and $t\in\efek$.
         \item If $r'\ne r$, see~(\ref{item:defaultmap}).
       \end{itemize}
    \item $e_k$ is an end-return edge, $r_1,\,\dots,\,r_k\in R$ are the local variables in the callee method, $r'$ is the receiver of the call site corresponding to the return node $n_k$, and $f$ is the called method with signature~$s$.
      Then 
      \[
        \varepsilon_R(e_k)=\lambda m\,.\,m[r'\to m(r')\cap\tau(s,\,f)][r_1\to\bot_T]\dots[r_k\to\bot_T].
      \]
      If $r\in\{r_1,\,\dots,\,r_k\}$, see~Case~\ref{item:asgn}. Otherwise, the case is analogous to Case~\ref{item:callstart}.
    \item\label{item:idcase} The node contains any other instruction.
      Then 
      \[
        \ccedgefn R(e_k)(\mpdkm)(r)=\id(\Delta)(r)=\Delta(r),
      \]
      which contains $t$ according to~\eqref{eq:deltaContainsT}.\qedhere
  \end{enumerate}
\end{proof}

@@

    Assume that $e_k$ is a end-return edge with a call on the receiver $r'\in R$ with a signature $s$ to a function $f$.
    \begin{align*}
      \ccedgefn R&(e_k)(\mpdkm)(r)\\
      &=\left(\lambda m\,.\,m[r'\to m(r)\cap\tau(s,\,f)][r_1\to\bot_T]\dots[r_l\to\bot_T]\right)(\mpdkm)(r)\\
      &=\left(\mpdkm[r'\to \uptau\cap\tau(s,\,f)][r_1\to\bot_T]\dots[r_l\to\bot_T]\right)(r)\,,
    \end{align*}
  where $r_1,\,\dots,r_l\in R$ are the local variables in the called method.

@@

    Otherwise, if $r=r'$, then $\efek=\uptau\cap\tau(s,\,f)$.

    According to Lemma~\ref{lem:sound1} and by the induction hypothesis, the runtime type $t$ of $r$ must be contained in $\mpdkm(r)=\uptau$. At the same time, by definition, $t$ is part of $\tau(s,\,f)$. Therefore, $t\in\uptau\cap\tau(s,\,f)\subseteq\efek$, which means that $\efek\ne\top_T$.

@@

For the following proofs, recall from Section~\ref{sec:ideToIfds} that the result of an IDE analysis maps a lattice element to each node in the exploded supergraph. Specifically, for an IDE problem $Q$, the result $\resultIDE(Q):\ N^*\to D\times L$ maps nodes of the supergraph to pairs of data-flow facts and lattice elements~\cite{sagiv1996precise}:
\begin{equation}\label{eq:ideresult}
  \resultIDE(Q)=\lambda n\,.\,\lambda d\,.\,\mvp{\textsf{Env}}(n,\,d))\,.
\end{equation}

@@

\begin{proof}[\textbf{Proof of Lemma~\ref{lem:sound}}] 
According to~\eqref{eq:ideresult}, we can rewrite~\eqref{eq:transCcDef} as
\begin{equation}\label{eq:transCcResultCc}
  \backCC(\resultIDE(\transCC_R(P)))(n)
  =\{d\,|\,\forall r\in R\,.\,\mvp{\textsf{Env}}(n,\,d))(r)\ne\top_T\}.
\end{equation}
\mtodo{TODO rest of proof!}
Let $\rho=\resultIDE(\transCC_R(P))$. Then
  \begin{align*}
    \backCC(\rho)(n)
    &=D_n^\Subset(\rho)\\
    &=\left\{d'\ |\ 
        d'\in\mvp F(n)\,\wedge\,\forall r\in R:\ \rho(n,\ d')(r)\ne\top_T\right\}.
  \end{align*}
  Since $\mvp F(n)=\bigsqcap_{q\in\ivp(n)}M_F(q)(\varnothing)$, and $p\in\ivp(n)$, it follows that
    \begin{align*}
      d&\in M_F(p)(\varnothing)\\&\subseteq\mvp F(n)\,.
    \end{align*}
  At the same time, for all receivers $r\in R$,
  \begin{align*}
    \rho(n,\,d)(r)
    &=\left(\bigsqcap_{q\in\ivp(n)}\mpddef q d\right)(r)\\
    &=\bigsqcap_{q\in\ivp(n)}\mpddef q d(r)\,.
  \end{align*}
  According to~Lemma~\ref{lem:sound3}, $\mpd(r)\ne\top_T$.
  Since $p\in\ivp(n)$,
  \begin{align*}
    \mpd(r)\subseteq\bigsqcap_{q\in\ivp(n)}\mpddef qd(r)\,.
  \end{align*}
  From $\bigsqcap_{q\in\ivp(n)}\mpddef qd(r)=\rho(n,\,d)(r)$ it follows that
  $\mpd(r)\subseteq\rho(n,\,d)(r)$.
  Therefore, $\rho(n,\,d)(r)\ne\top_T$, and $d\in D_n^\Subset(\rho)=\backCC(\rho)(n)$.
\end{proof}

@@

  Otherwise, there are four sub-cases.
  \begin{enumerate}
    \item $e_k$ is a call-start edge, $r'.c()$ is the call site at $n_{k-1}$ with signature $s$, $f$ is the called procedure, and $r'\in U$.
    Then
    \[
      \ccedgefn U(e_k)=\lambda m\,.\,\delta(m)[r'\to\delta(m)(r)\cap\tau(s,\,f)]\,.
    \]
    There are two sub-cases.
    \begin{enumerate}
      \item\label{item:callstartreceq} If $r=r'$, then, according to~\eqref{eq:edgefnU}, the resulting set of types 
        \[
          \ccedgefn U(q')(\topcc)(r)=\delta(\ccedgefn U(q)(\topcc))(r)\cap\tau(s,\,f).
        \]
        If $d_{k-1}=\Lambda$, then $\delta(\ccedgefn U(q)(\topcc))(r)=\botcc(r)=\bot_T$. If $d_{k-1}\ne\Lambda$, then $\delta(\ccedgefn U(q)(\topcc))(r)=\ccedgefn U(q)(\topcc)(r)=\uptau$. The set $\tau(s,\,f)$ is the same for either case.

        Therefore, the value of $\ccedgefn U(q')(\topcc)(r)$ has the same result regardless of $U$,
        which means that $\ccedgefn S(q')(\topcc)(r)=\ccedgefn{\{r\}}(q')(\topcc)(r)$, and the Lemma holds.
      \item\label{item:callstartrecneq} If $r\ne r'$, then
        \begin{equation}
          \ccedgefn U(q')(\topcc)(r)=\delta(\ccedgefn U(q)(\topcc))(r)\,,
        \end{equation}
        which, as we have seen in~Case~\eqref{item:callstartreceq}, does not depend on~$U$, and the Lemma holds.
    \end{enumerate}
    \item $e_k$ is an end-return edge, $r_1,\,\dots,\,r_l\in U$ are the local variables in the callee method, $r'.c()$ is the call corresponding to the return node at $n_k$, $f$ is the called method with signature $s$, and $r'\in U$.
    Then
    \[
      \ccedgefn U(e_k)=\lambda m\,.\,\delta(m)
      [r'\to\delta(m)(r)\cap\tau(s,\,f)]
      [r_1\to\bot_T]\ldots[r_l\to\bot_T]\,.
    \]
    There are three sub-cases.
    \begin{enumerate}
      \item\label{item:localvarrec} If $r\in\{r_1,\,\dots,\,r_l\}$, then regardless of the value of $U$,
      \[
        \ccedgefn U(q')(\topcc)(r)=\bot_T\,,
      \]
      and the Lemma holds.
      \item Otherwise, if $r=r'$, the case is analogous to Case~\eqref{item:callstartreceq}.
      \item If $r\notin\{r',\,r_1,\,\dots,\,r_l\}$, then see Case~\eqref{item:callstartrecneq}.
    \end{enumerate}
    \item $n_{k-1}$ contains an assignment for $r'\in U$. Then
    \[
      \ccedgefn U(e_k)=\lambda m\,.\,\delta(m)[r'\to\bot_T]\,.
    \]
    If $r=r'$, see Case~\eqref{item:localvarrec}. If $r\ne r'$, see Case~\eqref{item:callstartrecneq}.
    \item Otherwise,
    \[
      \ccedgefn U(e_k)=\lambda m\,.\,\delta(m)\,,
    \]
    and the case is analogous to Case~\eqref{item:callstartrecneq}.\qedhere
  \end{enumerate}
\end{proof}

@@

\begin{lemma}\label{lem:recindep} Let $P$ be an IFDS problem. Let $N^*$ be the supergraph for $P$, $D$ the set of data-flow facts, and $S\subseteq R$ a set of receivers.
  Then for any $n\in N^*$, $d\in D$, and receiver $r\in S$,
  \begin{equation}
    \resultIDE\left(\transCC_S(P)\right)(n)(d)(r)=
    \resultIDE(\transCC_{\{r\}}(P))(n)(d)(r)\,.
  \end{equation}
\end{lemma}
\begin{proof} Recall from Section~\ref{sec:bgide} that
\begin{equation}\label{eq:mvpdef}
  \mvp{\textsf{Env}}(n)=\bigsqcap_{q\in\ivp(n)}M_\textsf{Env}(q)(\top)
\end{equation}

  According to~\eqref{eq:ideresult}, \eqref{eq:mvpdef}, and~\eqref{eq:envTransToEdgeFnEdge},
  \begin{align}
    \resultIDE\left(\transCC_S(P)\right)(n)(d)(r)
    &=\mvp{\textsf{Env}}(n,\,d)(r)\notag\\
    &=\left(\bigsqcap_{q\in\ivp(n)}M_\textsf{Env}(q)(\Omega)(d)\right)(r)\notag\\
    &=\left(\bigsqcap_{q\in\ivp(n)}\bigsqcap_{q'\in\mathsf{RP}(q,\,d)}\ccedgefn S(q')(\topcc)\right)(r)\notag\\
    &=\bigcup_{q\in\ivp(n)}\bigcup_{q'\in\mathsf{RP}(q,\,d)}\ccedgefn S(q')(\topcc)(r)\,.\label{eq:resultThroughEdgefn}
  \end{align}
  Then from Lemma~\ref{lem:recindepedgefn},
  \begin{align*}
    \resultIDE\left(\transCC_S(P)\right)(n)(d)(r)
    &=\bigcup_{q\in\ivp(n)}\bigcup_{q'\in\mathsf{RP}(q,\,d)}\ccedgefn{\{r\}}(q')(\topcc)(r)\\
    &=\resultIDE\left(\transCC_{\{r\}}(P)\right)(n)(d)(r)\,.\qedhere
  \end{align*}
\end{proof}

The next lemma shows that the set of types to which a receiver is mapped in a correlated-calls lattice element can be represented as an intersection of static-type function applications $\tau(s_i,\,f_i)$.
\begin{lemma}\label{lem:edgefnThroughTaus}
  For an IFDS problem $P$, a node $n\in N^*$, and fact $d\in D$, let $p\in\mathsf{RP}(n,\,d)$ be a realizable path and $r\in R$ a receiver. Then there exists a non-negative number $\gamma$ of calls on the receiver $r$ with signatures $s_\gamma$ to the functions~$f_\gamma$, for which
  \[
    \ccedgefn{\{r\}}(p)(\topcc)(r)=
      \bigcap_{\gamma\ge0}\tau(s_\gamma,\,f_\gamma)\,.
  \]
\end{lemma}
\begin{proof}
  Let $p$ have the following form\footnote{It can be shown from the definition of a pointwise representation in~Sagiv et al.~\cite{sagiv1996precise} that in a realizable path, there is never an edge from a fact of the set $D$ to a $\Lambda$ fact. Therefore, we can represent $p$ as a sequence of nodes that has a prefix of $\Lambda$-fact nodes, after which all nodes are non-$\Lambda$ facts.}:
  \[
    p=[(\startmain,\,\Lambda),\,(n_1,\,\Lambda),\,\dots,\,(n_k,\,\Lambda),
       (n_{k+1},\,d_{k+1}),\,\dots,\,(n_{k+l},\,d_{k+l})]\,,
  \]
  where $l\ge1$ and the facts for all nodes up to $n_k$ are equal to $\Lambda$ and $d_{k+i}\in D$ for $0<i\le l$.

@@

  From~\eqref{eq:edgefndef} we can infer that
  \[
    \ccedgefn{\{r\}}(p)=
    \ccedgefn{\{r\}}(e_{k+l})
    \circ\ldots
    \circ\ccedgefn{\{r\}}(e_{k+2})
    \circ(\lambda m\,.\,\beta)
    \circ\id
    \circ\ldots
    \circ\id\,,
  \]
  where
  \[
    \beta=
    \begin{cases}
      \botcc[r\to\tau(s,\,f)]&\text{if $(n_k,\,n_{k+1})$ is a call-start or end-return edge, and}\\&\text{the call site $r.c()$ with signature $s$ to the function}\\
      &\text{$f$ corresponds to the call-start or end-return edge,}\\
      \botcc&\text{otherwise\footnotemark.}
    \end{cases}
  \]
  \footnotetext{Since $d_k=\Lambda$ and $d_{k+1}\ne\Lambda$, the micro function for the edge $e_{k+1} $ is equal to $\lambda m\,.\,\varepsilon_{\{r\}}(e_{k+1})(\botcc)$. From the definition of $\varepsilon_S$~\eqref{eq:varepsilon} we can see that the only case where $\varepsilon_{\{r\}}(e_{k+1})(m)$ would not be equal to $\botcc$ is when $e_{k+1}$ is call-start or end-return edge.}

@@

If $\beta=\botcc[r\to\tau(s,\,f)]$, then 
\[
  \ccedgefn{\{r\}}(p)(\topcc)(r)=\tau(s,\,f)\,,
\]
and $\gamma=1$.

@@

Otherwise,
\begin{align*}
  \ccedgefn{\{r\}}(e_{k+l+1})(\topcc)(r)&=\ccedgefn{\{r\}}(p)(\topcc)(r)\\
  &=\bigcap_{N}\tau(s_N,\,f_N)\,,
\end{align*}
and therefore $\gamma=N$.

Suppose that $e_{k+l+1}$ is a call-start edge with a call on the receiver $r$ with signature $s$ to a function $g$. Then, according to~\eqref{eq:varepsilon}, 
\[
  \ccedgefn{\{r\}}(e_{k+l+1})=\lambda m\,.\,m[r\to m(r)\cap\tau(s,\,g)]\,.
\]
Therefore,
\begin{align*}
  \ccedgefn{\{r\}}&(p')(\topcc)(r)\\
  &=\lambda m\,.\,m[r\to m(r)\cap\tau(s,\,g)]\left(\ccedgefn{\{r\}}(p)(\topcc)\right)(r)\\
  &=\ccedgefn{\{r\}}(p)(\topcc)(r)\cap\tau(s,\,g)\\
  &=\left(\bigcap_{N}\tau(s_N,\,f_N)\right)\cap\tau(s,\,g)\,,
\end{align*}
and the Lemma holds for $\gamma=N+1$.

@@

\begin{proof}[\textbf{Proof of Lemma~\ref{lem:onlycorrrec}}]
  By definition of $\backCC$,
  \begin{align*}
    \backCC(\resultIDE\left(\transCC_R(P)\right))
    &=\{d\,|\,\resultIDE(\transCC_R(P))(n)(d)=\ell,\,\forall r\,.\,\ell(r)\ne\top_T\}\\
    &=\{d\,|\,\forall r\in R,\,\resultIDE(\transCC_R(P))(n)(d)(r)\ne\top_T\}.
  \end{align*}
